An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex
1

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for the superior performance of Puck is that it filters out irrelevant results during the retrieval process rather than searching for more candidates. CAPS performs as well as Puck. In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason. 
	\textcolor{orange}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity. This makes single-attribute queries more difficult and degrades performance.}
%	First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal. Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.

>>>>

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for their superior performance is that they filter out irrelevant results during the retrieval process rather than searching for more candidates. In contrast, multi-attribute construction significantly degrades the performance of graph-based methods, for which we identify the primary reason. 
	\textcolor{orange}{For algorithms with tightly coupled attribute and graph structures, increasing the number of attributes during index construction increases graph complexity. This makes single-attribute queries more difficult and degrades performance.}
%	First, graph fragmentation necessitates searching multiple entry points, undermining the inherent advantage of efficient graph traversal. Second, multi-attribute processing increases the algorithms' intrinsic computational overhead and reduces the effectiveness of their core metric mechanisms, such as distance calculation.
	%FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.
